---
title: "Code for UserNetR"
author: "Douglas Luke"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Code for UserNetR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette contains the R code used to produce the network analyses, results, and figures in my
book: \emph{A User's Guide to Network Analysis in R}. 

Note that this code is provided as is, and may not work exactly as shown in the book,
depending on version changes of R, igraph, statnet and any other R packages; as well
as particular characteristics of the computer being used to run the code.

Note also that this vignette is provided mainly as a convenience so that book
readers do not have to type in every line of code themselves. However,
manually typing the code is actually the preferred way to \emph{learn}
the concepts and methods of network analysis in R. Copying and pasting
does not facilitate the type of experimentation, testing, and even
thinking that might be helpful!

Finally, within each chapter of the book, there may be subtle order
effects that are present which may cause later code chunks to fail
unless earlier chunks have been run.

# Chapter 2 - 5 Number Summary
## Setup

```{r, eval=FALSE}
library(statnet)
library(UserNetR)
data(Moreno)
```

## Simple plot
```{r, eval=FALSE}
gender <- Moreno %v% "gender"
plot(Moreno,vertex.col=gender+2,vertex.cex=1.2)
```

# Size
```{r, eval=FALSE}
network.size(Moreno)
summary(Moreno,print.adj=FALSE)
```

## Density
```{r, eval=FALSE}
den_hand <- 2*46/(33*32)
den_hand
gden(Moreno)
```

## Components
```{r, eval=FALSE}
components(Moreno)
lgc <- component.largest(Moreno,result="graph")
```

## Diameter
```{r, eval=FALSE}
gd <- geodist(lgc)
max(gd$gdist)
```

## Transitivity
```{r, eval=FALSE}
gtrans(Moreno,mode="graph")
```

